Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-20 Grassmannian_cells.tex
test

%\usepackage[marginal]{showlabels}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{claim}[theorem]{Claim}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{question}[theorem]{Question}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

@@

As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(n)}$, they are uniquely determined by its dimension vector. We use this fact and do not state the particular maps defining the lifts. In this example, we just state the support of the representation including those dimensions which are not one. We call it the quiver of the representations.

The representation $\tilde P_2$ is defined by the following quiver:

\begin{align*}
  \xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\(2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n}}[rrd] &&\vdots\\&&(1,\alpha_n)}
\end{align*}
The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$, can be obtained from this quiver by erasing the arrow $\alpha_i$ and the corresponding sink. In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $\alpha_{j_1},\ldots,\alpha_{j_l}$ and the corresponding sinks.

>>>>

%\usepackage[marginal]{showlabels}
%
\newtheorem{theorem}{Theorem}[section]
\newtheorem{claim}[theorem]{Claim}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{question}[theorem]{Question}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

@@

As the lifts of all (truncated) preprojectives are exceptional as representations of $\widetilde{K(n)}$, they are uniquely determined by their dimension vector.
We use this fact and do not state the particular maps defining the lifts.
In this example, we just state the support of the representation including those dimensions which are not one.
We call it the quiver of the representations.

The representation $\tilde P_2$ is defined by the following quiver:
\begin{align*}
  \xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\(2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n}}[rrd] &&\vdots\\&&(1,\alpha_n)}
\end{align*}
The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$, can be obtained from this quiver by erasing the arrow $\alpha_i$ and the corresponding sink. In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $\alpha_{j_1},\ldots,\alpha_{j_l}$ and the corresponding sinks.
